---
title: "FML Assignment1"
author: "Meghana(811298610)"
date: "2023-09-09"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

#Imported Forestfires dataset from https://archive.ics.uci.edu/dataset/162/forest+fires

```{r}

Value=read.csv("C:\\Users\\maggi\\Desktop\\forestfires.csv")
#value
#The above snippet outputs the data in the dataset of Forestfires

```

#The below code gives the descriptive statistics of the dataset that has mean,median,mode and the deviation so on..

```{r}
summary(Value)
#The above gives whole summary of the table

a=mean(Value$wind)
print(a)

b=median(Value$day)
print(b)

c=mode(Value$DC)
print(c)
```

#we have different transformations such as log,exponents,min-max and so on.In this I have transformed the variable into logarithmic form.

```{r}
valueData <- log(Value$wind)
valueData
```

#I have plotted the histogram graph of wind variable(Quantitative variable) and frequency.In this we will know how frequently the winds are moving at certain speeds.

```{r}
#plot(Value) This gives the default graphs
hist(Value$wind, main = "Wind Histogram",
     xlab = "Wind (m/s)", col = "purple")
```

#The below graph is the scatter plot between temperature and RH variables.Here we can know the outliers,data distribution and many.
```{r}

x=Value$temp
y=Value$RH
plot(x,y,xlim=c(1,10),main= "Temp-RH Scatter Plot", xlab = "Temp", ylab= "RH")

```
